---
output: pdf_document
---

#Results

```{r, echo = False}
load("../../data/lasso_model.RData")
load("../../data/OLS.RData")
load("../../data/all_ridge_mods.RData")
load("../../data/pcr_fit.RData")
load("../../data/plsr_model.RData")
library(xtable)
library(knitr)
```

##Ridge
We perform ridge regresssion on the centered Credit training data, and obtain the following result:
The best lambda equals `r best_lambda`, and the test mse is `r test_mse`.
The coefficient of fitting the full data is following:

```{r xtable1, results = 'asis', echo = FALSE, warning=FALSE, comment= FALSE, message=FALSE}
load("../../data/all_ridge_mods.RData")
ridgecoef <- xtable(ridge_coef)
print(ridgecoef)
```

##Lasso
Then we fit lasso regression on the centered Credit training data.
The best lambda is `r best_lambda`, and the lasso test MSE is `r lasso_mse`.
The refitting coefficients is the following:
```{r xtable2, results = 'asis', echo = FALSE, warning=FALSE, comment= FALSE, message=FALSE}
load("../../data/lasso_model.RData")
lassocoef <- xtable(lasso_coef)
print(lassocoef)
```
We observe some coefficients could reduce to zero because of the special regularizing term the lasso regression has.


##PCR
Now we use a different method, the principle component methods to fit on the training data. In this case, we think the optimal number of principle components used is `r pcr_best`, and the resulting test MSE is `r pcr_mse`.
The coefficients of PCR model refitting on full data set is:
```{r xtable3, results = 'asis', echo = FALSE, warning=FALSE, comment= FALSE, message=FALSE}
load("../../data/pcr_fit.RData")
pcrcoef <- xtable(pcr.coef)
print(pcrcoef)
```

##PLSR
We slightly change our method to PLSR. The optimal number of principle components is `r plsr_best`, and the resulting test MSE is `r plsr_mse`
The coefficient of refitting PLSR model on full dataset is:
```{r xtable4, results = 'asis', echo = FALSE, warning=FALSE, comment= FALSE, message=FALSE}
load("../../data/plsr_model.RData")
plsrcoef <- xtable(plsr_coef)
print(plsrcoef)
```

#OLS
At last we look at the ordinary least square regression:
The coefficients of the model that includes all predictors is:
```{r xtable5, results = 'asis', echo = FALSE, warning=FALSE, comment= FALSE, message=FALSE}
load("../../data/OLS.RData")
olscoef <- xtable(OLS_summary$coefficients)
print(olscoef)
```
The R-square is `r OLS_summary$r.squared`. The Residual Standard Error is `r OLS_summary$sigma`